\vskip-0.6in \Large Political Uncertainty

### 2015-03-19 GS-extension.tex
fix inequalities for vote buyer B
add notes about constraint for vote buyer B; also notes from today's chat with Sebastian

							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) + b(j) \geq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) + b(j) \geq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\alpha + a(j) + b(j)}{\beta} \geq j \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \geq z \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj

@@

									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \cdot \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right) - b(j) \right] dj
							\item If the realizations of $Z$ are i.i.d. and the bribes are independent across legislators, (I believe) this can be maximized pointwise.

@@

								  W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1

@@

@@

>>>>

							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) + b(j) \leq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) + b(j) \leq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\alpha + a(j) + b(j)}{\beta} \leq j \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \leq z \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj

@@

									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \left(1- \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)\right) - b(j) \right] dj \\
							\item If the realizations of $Z$ are i.i.d. and the bribes are independent across legislators, (I believe) this can be maximized pointwise--except for the constraint

@@

								  - W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1

@@

								as long as the constraint is satisfied.
										\item I don't know how decisions are made if the constraint binds---how the rationing happens
										\item If the constraint is not binding, vote buyer B will pay every single legislator (we could put in some kind of fixed cost of dealing with each legislator to short circuit this outcome)
										\item Perhaps there's something in equilibrium I'm not seeing yet that will reduce the number of legislators that are paid

@@

\newpage
Notes from 3/19 Skype chat (Kristy and Sebastian)
\begin{itemize}
	\item We can use the data we have to horse-race this model against other hypotheses about how lobbyists distribute bribes
		\begin{itemize}
			\item Allocate equally among legislators
			\item Groseclose Snyder with full information: only one side pays
			\item Our model with one dimension
				\begin{itemize}
					\item Could we use the econometric model to benchmark to one where uncertainty disappears? Or, as it does theoretically, does the model have to change completely?
				\end{itemize}
			\item Our model with multiple dimensions
		\end{itemize}
	\item We can think of this as looking for the effect of uncertainty on prices---we'd be pricing uncertainty relative to a model with uncertainty
		\begin{itemize}
			\item ``a metric in dollars of uncertainty''
			\item this is a model of vote buying under uncertainty
		\end{itemize}
	\item Given how different the environment with uncertainty is, Kristy should explore both the sequential model that parrots GS96 and a simultaneous model that is more like GH94 (menu auction)
	\item When mapping to the data, we're going to want to know from the model whether/when total contributions represent WTP.
		\begin{itemize}
			\item It clearly doesn't in the case of certainty. One side pays nothing; the other pays either as much as is necessary to shut down its opponent, or nothing at all the necessary amount exceeds WTP
			\item May be able to show it doesn't matter, that the proportion of total expenditures is a sufficient statistic
		\end{itemize}
	\item Finish writing the model, and then see if we can use the estimates we already have to write a first, very rough draft
\end{itemize}
